### 2020-09-18 README.Rmd
All done through CV

```{r, eval = run_scbi}
# SCBI
scbi_growth_df <- focal_vs_comp_scbi %>% 
  predict_bayesian_model(model_specs = scbi_specs, posterior_param = scbi_fit_model) %>% 
  right_join(scbi_growth_df, by = c("focal_ID" = "stemID"))

scbi_growth_df <- scbi_growth_df %>% 
  st_as_sf()

@@

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
scbi_growth_df %>% 
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 0.4) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```

>>>>

```{r, eval = run_scbi}
# SCBI
scbi_growth_df <- focal_vs_comp_scbi %>% 
  predict_bayesian_model(posterior_param = posterior_param_scbi) %>% 
  right_join(scbi_growth_df, by = c("focal_ID" = "stemID"))

@@

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
scbi_growth_df %>% 
  st_as_sf() %>%
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 0.4) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```
